Extreme heterogeneity of influenza virus infection in single cells

### 2018-01-13 paper/paper.tex
added new threshold to call infected cells

For the semi-supervised t-SNE clustering, we used Monocle's cell hierarchy function to bin cells into those with no viral mRNA, <2\% viral mRNA, between 2\% and 20\% viral mRNA, and >20\%. 
Candidate marker genes for t-SNE dimensionality reduction were then determined using the Monocle function markerDiffTable, excluding the effects of sample variation and the number of genes identified in a given cell, using a q-value cutoff of 0.01.
The specificity of these markers was determined using the function calculateMarkerSpecificity -- the top 40 markers were retained, and used to place populations in a two-dimensional plane based on tSNE dimensionality reduction.

>>>>

For the semi-supervised t-SNE clustering, we used Monocle's cell hierarchy function to bin cells into those with no viral mRNA, <2\% viral mRNA, between 2\% and 20\% viral mRNA, and >20\%. 
Candidate marker genes for t-SNE dimensionality reduction were then determined using the Monocle function markerDiffTable, excluding the effects of sample variation and the number of genes identified in a given cell, using a q-value cutoff of 0.01.
The specificity of these markers was determined using the function calculateMarkerSpecificity -- the top 50 markers were retained, and used to place populations in a two-dimensional plane based on tSNE dimensionality reduction.
